\huge{ \emph{Supplement to} Algorithms For Shaping a Particle Swarm\\ With a Shared Control Input Using Boundary Interaction}

### 2016-12-04 RA-L/theory.tex
some tiny typos
Updated Algorithm

%\begin{algorithm}
%\caption{GenerateDesired$x$-spacing($s_1,s_2,e_1,e_2,L$)}\label{alg:XControl}
%\begin{algorithmic}[1]
%\Require knowledge of starting $(s_1,s_2)$ and ending $(e_1,e_2)$ positions of  two robots. 
%$(0,0)$ is bottom corner, $s_1$ is topmost robot, 
% $L$ is length of the walls. Current robot positions are $(r_1,r_2)$.
%\State flag $\gets 0$
% \If {$ r_{1y}  \equiv r_{2y}$} 
%\State perturb $x$ values
%\State flag $\gets 1$
%\EndIf
%%\Ensure   $ r_{1y} - r_{2y}  \equiv s_{1y} - s_{2y} $   %$\Delta y(t) \equiv \Delta y(0)$ 
%\State $\epsilon \gets $ small number
%\State $ \Delta s_x  \gets r_{1x} - r_{2x} $
%\State $ \Delta e_x \gets e_{1x} - e_{2x} $
%\If {$\Delta e_x < 0 $ }
%\State move$( L-\epsilon-\max( r_{1x},r_{2x}) ,0)   $ \Comment{Near right wall}
%\Else 
%\State  move$ ( \epsilon-\min( r_{1x},r_{2x}),0 )    $ \Comment{Near left wall}
%\EndIf
%\State move$(0, -\min( r_{1y},r_{2y} ))$ \Comment{Move to bottom}
%\If {$\Delta e_x - (r_{1x} - r_{2x} ) > 0 $}
%\State move$(\min(|\Delta e_x - \Delta s_x |, L- r_{1x}), 0)$  \Comment{Move right}
%\Else
%\State move$(-\min(|\Delta e_x - \Delta s_x |, r_{1x}), 0)$\Comment{Move left}
%\EndIf 
%\State move$(0, \epsilon)$ \Comment{Move up}
%\If {$r_{1x} - r_{2x} \not\equiv \Delta e_x$} 
%\State GenerateDesired$x$-spacing($r_1,r_2,e_1,e_2,L$)
%\EndIf
%
% \If {$ flag == 1$} 
%\State unperturb $x$ values
%\EndIf
%
%\State  \Return $(r_1,r_2)$
%\end{algorithmic}
%\end{algorithm}
\begin{algorithm}
\caption{GenerateDesired spacing($s_1,s_2,e_1,e_2,L$)}\label{alg:XControl}
\begin{algorithmic}[1]
\Require knowledge of starting $(s_1,s_2)$ and ending $(e_1,e_2)$ positions of  two robots. 
$(0,0)$ is bottom corner, $s_1$ is topmost, leftmost robot, 
 $L$ is length of the walls. Current robot positions are $(r_1,r_2)$.
\State $\Delta e_y = e_2.y - e_1.y$
\State $\Delta e_x = e_2.x - e_1.x$
\If {$\Delta e_y \neq 0$}
\State $sign \gets \frac{|\Delta e_y|}{\Delta e_y}$
\Else
\State $sign \gets 0$
\EndIf
\State Move to $(-r_1.x , -\min(R_2.y , R_1.y+ \Delta e_y)+\epsilon)$
\State Move to $(-\min(|-r_2.x+ \Delta e_x|, r_2.x), sign \, \min(\max(r_1.y + \Delta e_y, r_2.y)-\epsilon,L-\epsilon)+ \epsilon)$
\If {$r_2.y \neq r_1.y$}
\State Move to $(\max(\epsilon, \Delta e_x- (r_2.x - r_1.x)), -\min(r_1.y , r_2.y))$
\State Move to $\Delta e_x , (|sign|-1) \epsilon$
\EndIf
\State Move to $(e_2.x - r_2.x, e_2.y - r_2.y)$
\end{algorithmic}
\end{algorithm}

>>>>

%\begin{algorithm}
%\caption{GenerateDesired$x$-spacing($s_1,s_2,e_1,e_2,L$)}\label{alg:XControl}
%\begin{algorithmic}[1]
%\Require knowledge of starting $(s_1,s_2)$ and ending $(e_1,e_2)$ positions of  two robots. 
%$(0,0)$ is bottom corner, $s_1$ is topmost robot, 
% $L$ is length of the walls. Current robot positions are $(r_1,r_2)$.
%\State flag $\gets 0$
% \If {$ r_{1y}  \equiv r_{2y}$} 
%\State perturb $x$ values
%\State flag $\gets 1$
%\EndIf
%%\Ensure   $ r_{1y} - r_{2y}  \equiv s_{1y} - s_{2y} $   %$\Delta y(t) \equiv \Delta y(0)$ 
%\State $\epsilon \gets $ small number
%\State $ \Delta s_x  \gets r_{1x} - r_{2x} $
%\State $ \Delta e_x \gets e_{1x} - e_{2x} $
%\If {$\Delta e_x < 0 $ }
%\State move$( L-\epsilon-\max( r_{1x},r_{2x}) ,0)   $ \Comment{Near right wall}
%\Else 
%\State  move$ ( \epsilon-\min( r_{1x},r_{2x}),0 )    $ \Comment{Near left wall}
%\EndIf
%\State move$(0, -\min( r_{1y},r_{2y} ))$ \Comment{Move to bottom}
%\If {$\Delta e_x - (r_{1x} - r_{2x} ) > 0 $}
%\State move$(\min(|\Delta e_x - \Delta s_x |, L- r_{1x}), 0)$  \Comment{Move right}
%\Else
%\State move$(-\min(|\Delta e_x - \Delta s_x |, r_{1x}), 0)$\Comment{Move left}
%\EndIf 
%\State move$(0, \epsilon)$ \Comment{Move up}
%\If {$r_{1x} - r_{2x} \not\equiv \Delta e_x$} 
%\State GenerateDesired$x$-spacing($r_1,r_2,e_1,e_2,L$)
%\EndIf
%
% \If {$ flag == 1$} 
%\State unperturb $x$ values
%\EndIf
%
%\State  \Return $(r_1,r_2)$
%\end{algorithmic}
%\end{algorithm}
\begin{algorithm}
\caption{GenerateDesired spacing($s_1,s_2,e_1,e_2,L$)}\label{alg:XControl}
\begin{algorithmic}[1]
\Require knowledge of starting $(s_1,s_2)$ and ending $(e_1,e_2)$ positions of  two robots. 
$(0,0)$ is bottom corner, $s_1$ is top-leftmost robot, 
 $L$ is length of the walls. Current robot positions are $(r_1,r_2)$.
\Ensure $(e_1, e_2) , (s_1, s_2)$ all have $\epsilon$ distance with the walls.
\State $epsilon \gets$ diameter of the robot
\State $\Delta e_y = e_2.y - e_1.y$
\State $\Delta e_x = e_2.x - e_1.x$
\If {$\Delta e_y \neq 0$}
\State $sign \gets \frac{|\Delta e_y|}{\Delta e_y}$
\Else
\State $sign \gets 0$
\EndIf
\State Move by $(-r_1.x , -\min(r_2.y , r_1.y+ \Delta e_y)+\epsilon)$ \Comment{Touch left wall}
\State Move by $(-\min(|-r_2.x+ \Delta e_x|, r_2.x), sign \, \min(\max(r_1.y + \Delta e_y, r_2.y)-\epsilon,L-\epsilon)+ \epsilon)$ \Comment{Adjust  $y$}
%\If {$r_2.y \neq r_1.y$}
\State Move by $(\max(\epsilon, \Delta e_x- (r_2.x - r_1.x)), -\min(r_1.y , r_2.y))$ \Comment{Touch bottom wall}
\State Move by $(\Delta e_x , (|sign|-1) \epsilon)$ \Comment{Adjust $x$}
%\EndIf
\If {$\Delta e_y \neq r_2.y - r_1.y$}
\State Move by $(L- r_1.x , \epsilon)$ \Comment{Touch Right wall}
\State Move by $(0, \Delta e_y - r_2.y)$ \Comment{Adjust $y$}
\EndIf
\State Move by $(e_2.x - r_2.x, e_2.y - r_2.y)$ \Comment{Go to the goal position}
\end{algorithmic}
\end{algorithm}
